Non-analogues in paleoecological reconstruction - the effects of analogue distance

### 2015-07-23 Paper_Markdown.Rmd
Removed the `md_document` flag in the output header.
Knit to PDF for most recent update.

---
title: "Non-analogues in paleoecological reconstruction - the effects of analogue distance"
author: "Simon Goring *et al*."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
    variant: markdown
  pdf_document:
    pandoc_args: "-V geometry:vmargin=1in -V geometry:hmargin=1in"
bibliography: non-analogue_clim.bib
csl: elsevier-harvard.csl
---
Non-analogues in paleoecological reconstruction - the effects of analogue distance
========================================================

>>>>

---
title: "Non-analogues in paleoecological reconstruction - the effects of analogue distance"
author: "Simon Goring *et al*."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    pandoc_args: "-V geometry:vmargin=1in -V geometry:hmargin=1in"
bibliography: non-analogue_clim.bib
csl: elsevier-harvard.csl
---
Non-analogues in paleoecological reconstruction - the effects of analogue distance
========================================================
